\documentclass[letterpaper,11pt]{article}

% ---------------- PACKAGES ----------------
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage[charter]{mathdesign}

% ---------------- MARGINS ----------------
\usepackage[margin=0.5in]{geometry}

\raggedright
\pagestyle{empty}
\setlength{\tabcolsep}{0pt}

% ---------------- SECTION STYLE ----------------
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\titlerule \vspace{-5pt}]

% ---------------- CUSTOM COMMANDS ----------------
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeHonorItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}
\newcommand{\resumeHonorsListStart}{\begin{itemize}[leftmargin=0in, label={}, itemsep=0pt, topsep=2pt]}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ================= DOCUMENT =================
\begin{document}

% ---------------- HEADER ----------------
\begin{center}
    {\Huge Harsh Haresh Shah} \\ \vspace{4pt} % [cite: 4]
    \small Stony Brook, New York 11790 \\ \vspace{2pt} % 
    \small 
    \faPhone\ (516) 434-1033 \quad 
    \faEnvelope\ \href{mailto:harsh@harsh.software}{\underline{harsh@harsh.software}} \quad % [cite: 1]
    \faLinkedin\ \href{https://linkedin.com/in/harsh-h-shah}{\underline{harsh-h-shah}} \quad % [cite: 1]
    \faGithub\ \href{https://github.com/Harsh-H-Shah}{\underline{Harsh-H-Shah}} \quad % [cite: 13]
    \faGlobe\ \href{https://harsh.software}{\underline{harsh.software}} % [cite: 13]
\end{center}

% ---------------- EDUCATION ----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Stony Brook University}{Aug 2024 -- May 2026} % [cite: 3, 14]
    {Master of Computer Science -- CGPA: 3.71/4.0}{Stony Brook, New York} % [cite: 5, 14]
    % \resumeItemListStart
    %     \resumeItem{\textbf{Relevant Coursework:} Algorithms, Operating Systems, Wireless Networks, Data Structures} % [cite: 6]
    % \resumeItemListEnd
  \resumeSubheading
    {University of Mumbai}{Dec 2020 -- May 2024} % [cite: 7, 15]
    {Bachelor of Engineering in Computer Engineering -- CGPA: 9.05/10}{Mumbai, India} % [cite: 8, 16]
    % \resumeItemListStart
    %     \resumeItem{\textbf{Relevant Coursework:} Databases, Computer Networks, Distributed Systems} % [cite: 9]
    % \resumeItemListEnd
\resumeSubHeadingListEnd

% ---------------- TECHNICAL SKILLS ----------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
    {\item{
     \textbf{Languages}:{ Python, Java, C++, JavaScript/TypeScript, SQL, Solidity, Bash/Shell, Dart} \\
     \textbf{Frameworks}:{ React, Node.js, Flask, Flutter, Spring Boot, PyTorch, Docker, Kubernetes, AWS, Azure, GCP} \\
     \textbf{Tools}:{ Linux/Unix, Git, CI/CD (GitHub Actions, Jenkins), Prometheus, Grafana, Kafka, gRPC, Prompt Engineering} \\
     \textbf{Databases}:{ PostgreSQL, MySQL, MongoDB, Redis, Vector Databases (Pinecone, Chroma)}
    }}
\end{itemize}
 

% ---------------- EXPERIENCE ----------------
\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Stony Brook University | Mechanismic Inc.}{Oct 2025 -- Present}
    {Graduate Software Research Assistant}{Stony Brook, New York}
    \resumeItemListStart
      \resumeItem{Built a PCI-DSS compliant subscription system using Stripe and GCP Cloud Functions, handling billing for \textbf{1,000+ users}.}
      \resumeItem{Integrated tiered access control in the SnappyXO-Auth package, maintaining permission check latency under \textbf{100ms}.}
      \resumeItem{Reduced manual support workload by \textbf{45\%} by automating the end-to-end license provisioning pipeline for subscriptions.}
    \resumeItemListEnd

  \resumeSubheading
    {Meta | Major League Hacking}{Jun 2025 -- Sep 2025}
    {Production Engineering Intern}{Remote}
    \resumeItemListStart
      \resumeItem{Deployed Flask application with Redis caching, Docker containers, and CI/CD via GitHub Actions on Digital Ocean VPS.}
      \resumeItem{Configured Linux infrastructure with Nginx load balancing and systemd service management to sustain \textbf{10k+ RPM traffic}.}
      \resumeItem{Implemented monitoring with Prometheus, Grafana, and Alertmanager, reducing incident detection time by \textbf{30\%}.}
    \resumeItemListEnd

  \resumeSubheading
    {Acapulco AI Services}{Oct 2023 -- Mar 2024}
    {Software Developer Intern}{Mumbai, India}
    \resumeItemListStart
      \resumeItem{Led the building of ZapMap (EV platform) using Flask, Flutter, PostgreSQL with PostGIS, Docker, and GitHub Actions.}
      \resumeItem{Optimized routing by implementing a custom A* algorithm with OpenStreetMap data, improving ETA accuracy by \textbf{25\%}.}
      \resumeItem{Designed microservices architecture and integrated third-party charging network APIs, achieving \textbf{99.5\%} API reliability.}
    \resumeItemListEnd

  \resumeSubheading
    {Aumsat Technologies}{Jun 2023 -- Oct 2023}
    {Software Developer Intern}{Mumbai, India}
    \resumeItemListStart
      \resumeItem{Engineered a geospatial ETL pipeline in Python using GeoPandas and GDAL to process and standardize \textbf{500+ datasets}.}
      \resumeItem{Automated data ingestion and validation, reducing processing latency by \textbf{40\%} and saving \textbf{10+} engineering hours per week.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

% ---------------- PROJECTS ----------------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Threat Detection Prototype — MetaMask} $|$ \emph{Ethereum, Browser Security, TypeScript} {\href{https://github.com/MetaMask/metamask-extension/pull/35825}{\scriptsize \faExternalLink*}}}{\textbf{Jan 2025 -- Dec 2025}}
    \resumeItemListStart
      \resumeItem{Analyzed address poisoning and typosquatting attacks, identifying patterns across \textbf{175K+} malicious transaction attempts.}
      \resumeItem{Prototyped low-latency detection heuristics (Damerau-Levenshtein distance, transaction history) that reduced phishing risk by \textbf{70\%} with only \textbf{30ms} overhead.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Alpha Trading — Real-Time Market Data System} $|$ \emph{React, WebSockets, AWS, LSTM} {\href{https://github.com/Harsh-H-Shah/Alpha-trading}{\scriptsize \faExternalLink*}}}{\textbf{Dec 2023 -- Mar 2024}}
    \resumeItemListStart
      \resumeItem{Built a real-time trading simulator consuming WebSocket feeds for \textbf{500+ NSE stocks}, with latencies under \textbf{100ms}.}
      \resumeItem{Integrated LSTM neural network for price trend forecasting, achieving \textbf{85\% accuracy} on historical data.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Rashi Pay — Offline Payment Interface} $|$ \emph{React Native, Express.js, Bluetooth, RSA}}{\textbf{Mar 2022 -- Aug 2022}}
    \resumeItemListStart
      \resumeItem{Created an offline P2P payment app using BLE, enabling offline transactions \textbf{40\% faster} than internet-dependent methods.}
      \resumeItem{Implemented end-to-end security with 2048-bit RSA encryption, with \textbf{10,000+} secure test transactions.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- HONORS & RECOGNITIONS -----------
\section{Honors \& Recognitions}
\resumeSubHeadingListStart
    \resumeHonorItem{\textbf{Won Smart India Hackathon 2022} $|$ among 30,000+ teams for developing RashiPay Offline Payment Interface.}
    \resumeHonorItem{\textbf{Finalist, Harbinger 2.0 RBI Hackathon} $|$ Among 363 teams from 22 countries for a scalable blockchain solution.}
    \resumeHonorItem{\textbf{Won HopperHacks 2025} and \textbf{HackNYU 2025} $|$ for accessibility applications.}
    \resumeHonorItem{\textbf{Publication, CSA 2024} $|$ "A Cloud-Based Architecture for EV Charge Station Finder with Efficient Scheduling."}
\resumeSubHeadingListEnd

\end{document}